Optimal control for selective electroporation of the viral envelope

### 2021-05-27 documents/pure_electroporation.tex
Swapped terms on virus_optimize.cxx, still no idea why
most promising yet
Introduced a bug somewhere

\title{Selective electroporation of the viral envelope}
\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
\date{\small{March 21 2021}}

@@

%mention the github again
\lettrine{A}{s} an addendum to a crude technical report \cite{notes2021} by the author, presenting some experimental results on an adjacent technique

@@

@@

@@

>>>>

\title{Optimal control for selective electroporation of the viral envelope}
\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
\date{\small{March 21 2021}}

@@

%mention the github again

\lettrine{A}{s} an addendum to a crude technical report \cite{notes2021} by the author, presenting some experimental results on an adjacent technique

@@

There appears to be an error in; the coefficients are in descending order, whereas they should be in ascending order. See

@@

%polarization? can we somehow twist the polarization?

@@

\subsection*{Limitations and next steps}

Involves careful control of the second derivative of a waveform
